Title

### 2015-12-10 paper/paper.tex
change set to sequence

From a high level, our system is a pipeline, which takes an AMR representation
of the information set that is to be communicated as input, and outputs a set
of AMR representations, which are the AMRs representing the sentences
containing all of the information in the information set.

>>>>

From a high level, our system is a pipeline, which takes an AMR representation
of the information set that is to be communicated as input, and outputs a
sequence of AMR representations, which are the AMRs representing the sentences
containing all of the information in the information set.
